\bf Probabilistic Forecasts in Hierarchical~Time~Series

### 2020-02-07 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Conclusion correction
Minor Puwasala changes
Blind and submission

%\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{1}

@@

\if1\blind
{
  \title{\bf Forecast reconciliation: A geometric view with new insights on bias correction}
  \author{Anastasios Panagiotelis\\
    Department of Econometrics and Business Statistics,\\
    Monash University, VIC 3145, Australia.\\
    Email: Anastasios.Panagiotelis@monash.edu \\[0.6cm]
    Puwasala Gamakumara\\
    Department of Econometrics and Business Statistics,\\
    Monash University, VIC 3800, Australia.\\
    Email: Puwasala.Gamakumara@monash.edu \\[0.6cm]
    George Athanasopoulos\thanks{Corresponding Author. The authors gratefully acknowledge the support of Australian Research Council Grant DP140103220. We also thank Professor Mervyn Silvapulle for valuable comments.}\hspace{.2cm}\\
    Department of Econometrics and Business Statistics,\\
    Monash University, VIC 3145, Australia.\\
    Email: George.Athanasopoulos@monash.edu \\[0.6cm]
    Rob J Hyndman\\
    Department of Econometrics and Business Statistics,\\
    Monash University, VIC 3800, Australia.\\
    Email: Rob.Hyndman@monash.edu\\[1.5cm]}
  \maketitle
} \fi

@@

The following theorem proves that the solution to this optimisation problem does not depend of the choice of $\bm{W}$ used in the loss function.
\begin{theo}[Expected loss minimisation and MinT]\label{th:gmint}
    The usual MinT reconciliation method $\tilde{\bm{y}}=\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}\hat{\bm{y}}$ solves the optimisation problem in Eq.~\eqref{eq:GMinTObj} for any choice of $\bm{W}$.
\end{theo}
\begin{proof}
	The loss function in Eq.~\eqref{eq:GMinTObj} is equivalent to Euclidean distance in the transformed space and can therefore be minimised by using the MinT method in this space. The MinT method in the transformed space is given by
	\begin{equation}
	\label{eq:MinTtran}
	\tilde{\bm{y}}^{*}=\bm{S}^{*}\left(\bm{S}^{*'}\bm{\Sigma}^{*-1}\bm{S}^{*}\right)^{-1}\bm{S}^{*'}\bm{\Sigma}^{*-1}\hat{\bm{y}}^{*}\,,
	\end{equation}
	where  $\bm{y}^{*}=\bm{W}^{1/2}\bm{y}$, $\bm{S}^{*}=\bm{W}^{1/2}\bm{S}$, $\hat{\bm{y}}^{*}=\bm{W}^{1/2}\hat{\bm{y}}$ and
	\begin{align*}
	\bm{\Sigma}^*&=E\left[(\bm{y}^{*}-\hat{\bm{y}}^{*})(\bm{y}^{*}-\hat{\bm{y}}^{*})'\right]\\
	&=E\left[\bm{W}^{1/2}(\bm{y}-\hat{\bm{y}})(\bm{y}-\hat{\bm{y}})'(\bm{W}^{1/2})'\right]\\
	&=\bm{W}^{1/2}E\left[(\bm{y}-\hat{\bm{y}})(\bm{y}-\hat{\bm{y}})'\right](\bm{W}^{1/2})'\\
	&=\bm{W}^{1/2}\bm{\Sigma}(\bm{W}^{1/2})'
	\end{align*}
	Noting that
	\begin{align*}
	(\bm{\Sigma}^{*})^{-1}&=\left(\bm{W}^{1/2}\bm{\Sigma}(\bm{W}^{1/2})'\right)^{-1}\\
	&=(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{-1/2}\\
	\end{align*}
	and substituting the expressions for $\bm{\Sigma}^*$, ${\bm{S}^*}$, $\bm{y}^{*}$ and $\hat{\bm{y}}^{*}$ into Eq.~\eqref{eq:MinTtran} yields,
	\begin{align*}
	\bm{W}^{1/2}\tilde{\bm{y}}=\bm{W}^{1/2}\bm{S}&\left((\bm{W}^{1/2}\bm{S})'(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{-1/2}\bm{W}^{1/2}\bm{S}\right)^{-1}\\
	&(\bm{W}^{1/2}\bm{S})'(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{-1/2}\bm{W}^{1/2}\hat{\bm{y}}
	\end{align*}
	Rearranging and cancelling gives
	\begin{align*}
    \tilde{\bm{y}}&=\bm{S}\left(\bm{S}'(\bm{W}^{1/2})'(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{-1/2}\bm{W}^{1/2}\bm{S}\right)^{-1}\\
    &\qquad\qquad\bm{S}'(\bm{W}^{1/2})'(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{-1/2}\bm{W}^{1/2}\hat{\bm{y}}\\
	&=\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}\hat{\bm{y}}\\
	\end{align*}
	which corresponds to the usual MinT method.
\end{proof}

@@

Defining concepts such as coherence and reconciliation in geometric terms provides new insights into hierarchical forecasting methods. {\color{blue} We recommend the following steps for practitioners.
\begin{enumerate}
	\item Choose an objective, either
	\begin{enumerate}[a.]
		\item To guarantee that reconciled forecasts improve upon base forecasts.
		\item To find the reconciliation method that is best on average.
	\end{enumerate}
    \item Select a $\bm{W}$ to use in loss function $L^2_{\bm{W}}$ that is well suited to the empirical problem.  For objective (a) our results also apply to any monotonic function of $L^2_{\bm{W}}$.
    \item Select a reconciliation method.
    \begin{itemize}
    	\item For objective (a) this should be $\bm{G}=(\bm{S}'\bm{W}\bm{S})^{-1}\bm{S}'\bm{W}$. The dependencies between forecast errors is not relevant.
    	\item For objective (a) this should be $\bm{G}=(\bm{S}'\bm{\Sigma}^{-1}\bm{S})^{-1}\bm{S}'\bm{\Sigma}^{-1}$. The choice of $\bm{W}$ is not relevant.
    \end{itemize}
\end{enumerate}}
{\color{blue} Furthermore, for the second objective, base forecasts must be unbiased.  We recommend carrying out} bias correction before reconciliation {\color{blue} and provide evidence that this} improves forecast accuracy compared to approaches that do not bias correct and/or do not use reconciliation.

>>>>

%\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{0}

@@

\if1\blind
{
  \title{\bf Forecast reconciliation: A geometric view with new insights on bias correction}
  \author{Anastasios Panagiotelis\thanks{Corresponding Author. The authors gratefully acknowledge the support of Australian Research Council Grant DP140103220. We also thank Professor Mervyn Silvapulle for valuable comments.}\hspace{.2cm}\\
    Department of Econometrics and Business Statistics,\\
    Monash University, VIC 3145, Australia.\\
    Email: Anastasios.Panagiotelis@monash.edu \\[0.6cm]
    George Athanasopoulos\\
    Department of Econometrics and Business Statistics,\\
    Monash University, VIC 3145, Australia.\\
    Email: George.Athanasopoulos@monash.edu \\[0.6cm]
    Puwasala Gamakumara\\
    Department of Econometrics and Business Statistics,\\
    Monash University, VIC 3800, Australia.\\
    Email: Puwasala.Gamakumara@monash.edu \\[0.6cm]
    Rob J Hyndman\\
    Department of Econometrics and Business Statistics,\\
    Monash University, VIC 3800, Australia.\\
    Email: Rob.Hyndman@monash.edu\\[1.5cm]}
  \maketitle
} \fi

@@

The following theorem proves that the solution to this optimisation problem does not depend on the choice of $\bm{W}$ used in the loss function.
\begin{theo}[Expected loss minimisation and MinT]\label{th:gmint}
    The usual MinT reconciliation method $\tilde{\bm{y}}=\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}\hat{\bm{y}}$ solves the optimisation problem in Eq.~\eqref{eq:GMinTObj} for any choice of $\bm{W}$.
\end{theo}
\begin{proof}
	The loss function in Eq.~\eqref{eq:GMinTObj} is equivalent to Euclidean distance in the transformed space and can therefore be minimised by using the MinT method in this space. The MinT method in the transformed space is given by
	\begin{equation}
	\label{eq:MinTtran}
	\tilde{\bm{y}}^{*}=\bm{S}^{*}\left(\bm{S}^{*'}\bm{\Sigma}^{*-1}\bm{S}^{*}\right)^{-1}\bm{S}^{*'}\bm{\Sigma}^{*-1}\hat{\bm{y}}^{*}\,,
	\end{equation}
	where  $\bm{y}^{*}=\bm{W}^{1/2}\bm{y}$, $\bm{S}^{*}=\bm{W}^{1/2}\bm{S}$, $\hat{\bm{y}}^{*}=\bm{W}^{1/2}\hat{\bm{y}}$ and
	\begin{align*}
	\bm{\Sigma}^*&=E\left[(\bm{y}^{*}-\hat{\bm{y}}^{*})(\bm{y}^{*}-\hat{\bm{y}}^{*})'\right]\\
	&=E\left[\bm{W}^{1/2}(\bm{y}-\hat{\bm{y}})(\bm{y}-\hat{\bm{y}})'(\bm{W}^{1/2})'\right]\\
	&=\bm{W}^{1/2}E\left[(\bm{y}-\hat{\bm{y}})(\bm{y}-\hat{\bm{y}})'\right](\bm{W}^{1/2})'\\
	&=\bm{W}^{1/2}\bm{\Sigma}(\bm{W}^{1/2})'
	\end{align*}
	Noting that
	\begin{align*}
	(\bm{\Sigma}^{*})^{-1}&=\left(\bm{W}^{1/2}\bm{\Sigma}(\bm{W}^{1/2})'\right)^{-1}\\
	&=(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{-1/2}\\
	\end{align*}
	and substituting the expressions for $\bm{\Sigma}^*$, ${\bm{S}^*}$, $\bm{y}^{*}$ and $\hat{\bm{y}}^{*}$ into Eq.~\eqref{eq:MinTtran} yields,
	\begin{align*}
	\bm{W}^{1/2}\tilde{\bm{y}}=\bm{W}^{1/2}\bm{S}&\left((\bm{W}^{1/2}\bm{S})'(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{-1/2}\bm{W}^{1/2}\bm{S}\right)^{-1}\\
	&(\bm{W}^{1/2}\bm{S})'(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{-1/2}\bm{W}^{1/2}\hat{\bm{y}}
	\end{align*}
	Rearranging and cancelling gives
	\begin{align*}
    \tilde{\bm{y}}&=\bm{S}\left(\bm{S}'(\bm{W}^{1/2})'(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{-1/2}\bm{W}^{1/2}\bm{S}\right)^{-1}\\
    &\qquad\qquad\bm{S}'(\bm{W}^{1/2})'(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{-1/2}\bm{W}^{1/2}\hat{\bm{y}}\\
	&=\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}\hat{\bm{y}}\\
	\end{align*}
	which corresponds to the usual MinT method.
\end{proof}

@@

Defining concepts such as coherence and reconciliation in geometric terms provides new insights into hierarchical forecasting methods. {\color{blue} We recommend the following steps for practitioners.
\begin{enumerate}
	\item Choose an objective, either
	\begin{enumerate}[a.]
		\item To guarantee that reconciled forecasts improve upon base forecasts.
		\item To find the reconciliation method that is best on average.
	\end{enumerate}
    \item Select a $\bm{W}$ to use in loss function $L^2_{\bm{W}}$ that is well suited to the empirical problem.  For objective (a) our results also apply to any monotonic function of $L^2_{\bm{W}}$.
    \item Select a reconciliation method.
    \begin{itemize}
    	\item For objective (a) this should be $\bm{G}=(\bm{S}'\bm{W}\bm{S})^{-1}\bm{S}'\bm{W}$. The dependencies between forecast errors is not relevant.
    	\item For objective (b) this should be $\bm{G}=(\bm{S}'\bm{\Sigma}^{-1}\bm{S})^{-1}\bm{S}'\bm{\Sigma}^{-1}$. The choice of $\bm{W}$ is not relevant.
    \end{itemize}
\end{enumerate}}
{\color{blue} Furthermore, for the second objective, base forecasts must be unbiased.  We recommend carrying out} bias correction before reconciliation {\color{blue} and provide evidence that this} improves forecast accuracy compared to approaches that do not bias correct and/or do not use reconciliation.

### 2020-02-07 R1/Letter.tex
Changed date
Blind and submission

%\makelabels
\begin{document}
 \begin{letter}{To: Pierre Pinson\\
 	Editor, International Journal of Forecasting\\
 	DTU Elektro\\
 	348, {\O}rsteds Pl., \\
 	2800 Kongens Lyngby, Denmark}
    From: George Athanasopoulos\\
    Department of Econometrics and Business Statistics\\
    Monash University\\
    Melbourne, VIC, 3800, Australia

 \opening{ March 12, 2018\\ \\Dear Professor Pinson,}
%\textbf{RE: Revision for Computational and Graphical Statistics by Tan Ban Kheng, Anastasios
%	Panagiotelis and George Athanasopoulos}
 \medskip

Please find attached a revised manuscript for ``Forecast reconciliation: a geometric view with new insights on bias correction" by Anastasios Panagiotelis, Puwasala Gamakumara, George Athanasopoulos and Rob Hyndman for your consideration for publication in International Journal of Forecasting. We are very excited to have been given the opportunity to revise and resubmit. We carefully considered the comments offered by the two reviewers. Herein, we briefly summarize the major changes in the revision:
\begin{enumerate}
	\item We introduce a new result about MinT that explicitly makes the connection between trace minimisation and minimising a loss function based on squared Euclidean distance.  We also prove a new result that MinT minimises expected loss for loss functions based on squared generalised Euclidean distance.  This result is demonstrated in an expanded empirical application in section 5.2 that includes a wider range of loss functions. 
	\item We have greatly expanded the empirical study of Section 5.3 including more measures of forecast accuracy (including one specifically measuring bias).  This has led to the insight that reconciliation alone can in fact reduce the bias of an estimator.  We also now also report where differences in forecast accuracy are statistically significant.
	\item We now reflect on some issues that were not discussed in the previous version of the manuscript including the role of non-negative forecasts, and state-space models. 
\end{enumerate}

>>>>

%\makelabels
\begin{document}
 \begin{letter}{To: Michael McCracken\\
 	Handling Editor, International Journal of Forecasting
    }
    From: George Athanasopoulos\\
    Department of Econometrics and Business Statistics\\
    Monash University\\
    Melbourne, VIC, 3800, Australia

 \opening{\today\ \\Dear Mike,}
%\textbf{RE: Revision for Computational and Graphical Statistics by Tan Ban Kheng, Anastasios
%	Panagiotelis and George Athanasopoulos}
 \medskip

Please find attached a revised manuscript for ``Forecast reconciliation: a geometric view with new insights on bias correction" by Anastasios Panagiotelis, George Athanasopoulos, Puwasala Gamakumara, and Rob Hyndman for your consideration for publication in International Journal of Forecasting. We are very excited to have been given the opportunity to revise and resubmit. We carefully considered the comments offered by the two reviewers. Herein, we briefly summarize the major changes in the revision:
\begin{enumerate}
	\item We introduce a new result about MinT that explicitly makes the connection between trace minimisation and minimising a loss function based on squared Euclidean distance. We also prove a new result that MinT minimises expected loss for loss functions based on squared generalised Euclidean distance.  This result is demonstrated in an expanded empirical application in Section 5.2 that includes a wider range of loss functions.
	\item We have greatly expanded the empirical study of Section 5.3 including more measures of forecast accuracy (including one specifically measuring bias). This has led to the insight that reconciliation alone can in fact reduce the bias of an estimator. We also now also report where differences in forecast accuracy are statistically significant.
	\item We now reflect on some issues that were not discussed in the previous version of the manuscript including the role of non-negative forecasts, and state-space models.
\end{enumerate}
